ECCCos from the Black Box: Letting Models speak for Themselves

### 2023-04-26 paper/paper.tex
added pseudo code

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

\begin{algorithm}
  \caption{An algorithm with caption}\label{alg:cap}
  \begin{minipage}[t]{0.45\textwidth}
  \begin{algorithmic}
    \Require $n \geq 0$
    \Ensure $y = x^n$
    \State $y \gets 1$
    \State $X \gets x$
    \State $N \gets n$
    \While{$N \neq 0$}
    \If{$N$ is even}
        \State $X \gets X \times X$
        \State $N \gets \frac{N}{2}$  \Comment{This is a comment}
    \ElsIf{$N$ is odd}
        \State $y \gets y \times X$
        \State $N \gets N - 1$
    \EndIf
    \EndWhile
  \end{algorithmic}
  \end{minipage}
\end{algorithm}

@@

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\begin{minipage}[c]{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{../artifacts/results/images/surrogate_gone_wrong.png}
  \captionof{figure}{Using surrogates can improve plausibility, but also increases vulnerability. Counterfactuals for turning an 8 (eight) into a 3 (three): original image (left); counterfactual produced using REVISE \citep{joshi2019realistic} with a well-specified surrogate (centre); and a counterfactual produced using REVISE \citep{joshi2019realistic} with a poorly specified surrogate (right).} \label{fig:vae}
\end{minipage}  
\hfill
\begin{minipage}[c]{0.45\textwidth}
\captionof{algorithm}{Generating ECCCos (For more details, see Appendix~\ref{app:eccco})}\label{alg:eccco}
\begin{algorithmic}[1]
  \Require $\mathbf{x}, \mathbf{y}^*, M_{\theta}, f, \Lambda, \alpha, \mathcal{D}, T, \eta, m, M$ \linebreak where $M_{\theta}(\mathbf{x})\neq\mathbf{y}^*$
  \Ensure $\mathbf{x}^\prime$
  \State Initialize $\mathbf{z}^\prime \gets f^{-1}(\mathbf{x})$
  \State Run \textit{SCP} for $M_{\theta}$ using $\mathcal{D}$
  \State Generate buffer $\mathcal{B}$ of $M$ conditional samples $\hat{\mathbf{x}}_{\theta}|\mathbf{y}^*$ using SGLD (Equation~\ref{eq:sgld})
  \State Initialize $t \gets 0$
  \While{\textit{not converged} or $t < T$}
  \State $\hat{\mathbf{x}}_{\theta, t} \gets \text{rand}(\mathcal{B},m)$
  \State $\mathbf{z}^\prime \gets \mathbf{z}^\prime - \eta \nabla_{\mathbf{z}^\prime} \mathcal{L}(\mathbf{z}^\prime,\mathbf{y}^*,\hat{\mathbf{x}}_{\theta, t})$
  \State $t \gets t+1$
  \EndWhile
  \State $\mathbf{x}^\prime \gets f(\mathbf{z}^\prime)$
\end{algorithmic}
\end{minipage}

@@

\subsection{Conformal Prediction}\label{app:eccco}
